WARNING!!!
ENVIROMENT WIPE CHUNK!!!
RUN WITH CARE!!!!

```{r}
rm(list=ls())
```

package auto install

```{r}
# Required packages

# Package names
packages <- c("tidyverse", "here", "lubridate", "testthat")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

invisible(sapply(packages, library, character.only = TRUE))

## cleanup
rm(installed_packages, packages)

```


data loading (place two files in project directory and rename as appropriate)
```{r}
broker1 <- read.csv(here("broker1.csv"))
broker2 <- read.csv(here("broker2.csv"))
```

variable names standardization
```{r}
##STANDERDISED VARIABLE NAMES
variable_names_standardised <- c("policy_id_number", 
                                 "amount", 
                                 "start", 
                                 "end", 
                                 "admin_cost", 
                                 "description", 
                                 "event", 
                                 "client_catagory", 
                                 "client_id", 
                                 "commission", 
                                 "activation_date", 
                                 "insurance_id", 
                                 "tax_amount", 
                                 "coverage_cost", 
                                 "policy_fee", 
                                 "policy_type", 
                                 "insurer", 
                                 "insurance_plan", 
                                 "renewal", 
                                 "root_policy_referance")

##ASSERT ORDER OF VARIABLES
broker1 <- broker1 %>% select(
  "PolicyNumber",
  "InsuredAmount",
  "StartDate",
  "EndDate",
  "AdminFee",
  "BusinessDescription",
  "BusinessEvent",
  "ClientType",
  "ClientRef",
  "Commission",
  "EffectiveDate",
  "InsurerPolicyNumber",
  "IPTAmount",
  "Premium",
  "PolicyFee",
  "PolicyType",
  "Insurer",
  "Product",
  "RenewalDate",
  "RootPolicyRef")

broker2<-broker2%>%select(
  "PolicyRef",
  "CoverageAmount",
  "InitiationDate",
  "ExpirationDate",
  "AdminCharges",
  "CompanyDescription",
  "ContractEvent",
  "ConsumerCategory",
  "ConsumerID",
  "BrokerFee",
  "ActivationDate",
  "InsuranceCompanyRef",
  "TaxAmount",
  "CoverageCost",
  "ContractFee",
  "ContractCategory",
  "Underwriter",
  "InsurancePlan",
  "NextRenewalDate",
  "PrimaryPolicyRef")

##REPLACE VARIABLE NAMES
colnames(broker1) <- variable_names_standardised
colnames(broker2) <- variable_names_standardised
```



data standardization
########################################################################

prefix function
```{r}
##function which extracts Id numbers, normalizes them and adds a uniform prefix.
number_ext3_prefix = function(data, prefix) {
  str_replace_all(data, "[[:alpha:]\\s\\t]", "") %>% 
  str_pad(3, side = "left", pad = "0") %>%
  paste0(prefix, x = .)
}
```
prefix function variables implimentation
```{r}
## standardize policy_id_number
broker1$policy_id_number <- broker1$policy_id_number %>% number_ext3_prefix("POL")
broker2$policy_id_number <- broker2$policy_id_number %>% number_ext3_prefix("POL")
```
```{r}
## standardize client ID (ASSUMPTION THAT CLIENT NUMBER IS THE IDENTIFIER IRRESPECTIVE OF LETTER PREFIX)
## do not run chunk if client_id should not be standardized this way
broker1$client_id <- broker1$client_id %>% number_ext3_prefix("CID")
broker2$client_id <- broker2$client_id %>% number_ext3_prefix("CID")
```
```{r}
## INSURANCE ID
broker1$insurance_id <- broker1$insurance_id %>% number_ext3_prefix("IPN")
broker2$insurance_id <- broker2$insurance_id %>% number_ext3_prefix("IPN")
```
```{r}
## root_policy_referance
broker1$root_policy_referance <- broker1$root_policy_referance %>% number_ext3_prefix("RP")
broker2$root_policy_referance <- broker2$root_policy_referance %>% number_ext3_prefix("RP")
```

```{r}
## description standardization (assumes this is relevant format for the sake of the test)
## INSURER DOES NOT APPEAR TO BE A FEILD IN NEED OF STANDERDISATION DISPITE SIMMILAR FORMAT
## do not run chunk if description need not be standardized.
## duplicate code and modify REGEX and target if insurer needs to be standardized too

broker1$description <- broker1$description %>% str_extract("([[:alnum:]]+)$") %>%
  paste0("Buisness ", x = .)
broker2$description <- broker2$description %>% str_extract("([[:alnum:]]+)$") %>%
  paste0("Buisness ", x = .)
```

numeric value assertions
```{r}
numeric_variables <- c("amount", "admin_cost", "commission", "tax_amount", "coverage_cost", "policy_fee")

for(i in numeric_variables) {
  broker1[i] <- as.numeric(broker1[[i]])
  broker2[i] <- as.numeric(broker2[[i]])
}

rm(numeric_variables, i)
```

conversion of date time values to date objects.
```{r}
date_variables = c("start", "end", "activation_date", "renewal")

for(i in date_variables) {
  broker1[i] <- as_date(dmy(broker1[[i]]))
  broker2[i] <- as_date(dmy(broker2[[i]]))
}

rm(date_variables, i)
```

event standardization
```{r}
## overview of categorical variables
#print(unique(broker1$event))
#print(unique(broker2$event))

##new policies
x <- str_which(broker1$event, "^(New)\\s|^(new)\\s|initiation|Initiation")
broker1[x, "event"] <- "New"
rm(x)
x <- str_which(broker2$event, "^(New)\\s|^(new)\\s|initiation|Initiation")
broker2[x, "event"] <- "New"
rm(x)

##renewals
x <- str_which(broker1$event, ".*renew.*|.*Renew.*|.*renewal.*|.*Renewal.*")
broker1[x, "event"] <- "Renewal"
rm(x)
x <- str_which(broker2$event, ".*renew.*|.*Renew.*|.*renewal.*|.*Renewal.*")
broker2[x, "event"] <- "Renewal"
rm(x)

## policy updates (possibly identical to renewals, but kept separate due to possible difference, edit as needed)
x <- str_which(broker1$event, ".*update.*|.*Update.*")
broker1[x, "event"] <- "Update"
rm(x)
x <- str_which(broker2$event, ".*update.*|.*Update.*")
broker2[x, "event"] <- "Update"
rm(x)
```

Insurance plan should not need standardizing due to plan type being available

############################################################
END OF DATA STANDERDISATION


data aggregation

```{r}
## create broker identification
broker1$broker_ID <- "broker1"
broker2$broker_ID <- "broker2"
broker_fused <- rbind(broker1, broker2)
```


data integrity verification
```{r}
## count NA values across data set for manual review and specify affected variables
broker_fused %>% summarise_all(funs(sum(is.na(.)))) %>% select_if(colSums(.) != 0)

## there are two missing entries across the dataset in start date and coverage cost
```



data analysis
###################################################################

```{r}
## calculates policy duration
broker_fused$policy_duration <- broker_fused$end - broker_fused$start
## calculates if policy is active
broker_fused <- broker_fused %>% mutate(active_policy = start<Sys.Date()&renewal>Sys.Date())

## active policy subset
broker_fused %>% filter(active_policy == TRUE) -> active_policies
```



total policy count
```{r}
number_of_policies <- length(unique(broker_fused$policy_id_number))

invisible(length(broker_fused$policy_id_number) - number_of_policies) 
# there is one repeated entry in the data set

## Manuel investigation shoes the duplicated policy number is POL040 which are both separate policies.
## this duplication was not caused by a coercion.
## suggest reassigning a new policy ID to one of the two.

##result
number_of_policies ## 60 unique policies
```
total customer count
```{r}
number_of_clients <- length(unique(broker_fused$client_id))

##result
number_of_clients ## 49 unique clients
```
total insurance amount
```{r}
total_insurance_amount <- sum(broker_fused$amount)

##result
total_insurance_amount ## 46637000 (currency and units not specified)
```
average policy duration
```{r}
broker_fused %>% summarise(mean(policy_duration, na.rm = TRUE)) -> average_policy_duration

##result
average_policy_duration ## 365.3333 days	
```
cleanup____________________________________________________________________________________
```{r}
rm(average_policy_duration, number_of_clients, number_of_policies, total_insurance_amount)
```


---------------------------ACTIVE POLICIES---------------------------------


total number of active policies per broker
```{r}
active_policies %>% 
  group_by(broker_ID) %>% 
  summarise(length(unique(policy_id_number)))
```

total number of active clients per broker
```{r}
active_policies %>% 
  group_by(broker_ID) %>% 
  summarise(length(unique(client_id)))
```

total amount handled by each broker for active policies (units not specified)
```{r}
active_policies %>%
  group_by(broker_ID) %>%
  summarise(sum(amount, na.rm = TRUE))
```

average active policy duration by broker
```{r}
active_policies %>% 
  group_by(broker_ID) %>% 
  summarise(mean(policy_duration, na.rm = TRUE))
```
#########################################
end of analysis



broker look-up module
```{r}
broker_lookup = "broker1" ## type broker ID here

broker_fused %>% filter(broker_ID == broker_lookup)
```



function unit test (i should have really used anything other than an RMD file for this)

```{r}
test_that("the prefix function works", {
  expect_equal(number_ext3_prefix("POLICY5", "POL"), "POL005")
  expect_equal(number_ext3_prefix("POLICY50", "POL"), "POL050")
  expect_equal(number_ext3_prefix("POLicy 5", "POL"), "POL005")
  expect_equal(number_ext3_prefix("abc 50", "POL"), "POL050")
  expect_equal(number_ext3_prefix("POLICY  5", "POL"), "POL005")
  expect_equal(number_ext3_prefix("POLICY  50", "POL"), "POL050")
  expect_equal(number_ext3_prefix("POLICY500", "POL"), "POL500")
  expect_equal(number_ext3_prefix("POLICY 500", "POL"), "POL500")
  expect_equal(number_ext3_prefix("5", "POL"), "POL005")
  expect_equal(number_ext3_prefix("", "POL"), "POL000")
  expect_equal(number_ext3_prefix("500 policy", "POL"), "POL500")
}) 
## weakness identified that larger numbers are not cut down to standard, however the formatting is consistent and can be adjusted easily

### reload for sake of test
broker1 <- read.csv(here("broker1.csv"))
broker2 <- read.csv(here("broker2.csv"))

test_that("colnames are of propper length", {
  expect_equal(ncol(broker1), length(variable_names_standardised))
  expect_equal(ncol(broker2), length(variable_names_standardised))
  expect_equal(ncol(broker2), ncol(broker1))
})

##given lack of functions, i can describe some ideas for robust code
## assert column name standardization is the same length as the source data set col names
## assert source data sets have the same number of columns
## check categorical "event variable for any un-categorized values"
## investigate behavior of injecting NA values, some functions already deal with this

```

FINAL PRODUCT
```{r}
broker_fused
```

